Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Make more small changes to simulation text

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each procedure.  In 
Panel A, all the intervals produced by the two robust estimators are reasonably close to 
their nominal coverage, although they slightly under cover the true treatment effect.
Our proposed bootstrap procedure consistently performs well, as it is about a percentage point 
closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
analytical interval has coverage as low as 31\% (in the second DGP) and never
higher than 86\%.

Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI Length,'' indicates that intervals from the
 two robust procedures have average lengths close to each other, while interval from the naive procedure has much shorter length on average.

These are DGPs where the naive confidence intervals are known to perform poorly, 
and this set of simulation results indicates that our proposed bootstrap approach is 
quite competitive with analytical methods for producing robust intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs
and performs similarly well compared to the analytical bias correction procedures proposed by CCT.

>>>>

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for
the analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each procedure.  In 
Panel A, all the intervals produced by the two robust estimators are reasonably close to 
their nominal coverage, although they slightly under-cover the true treatment effect.
Our proposed bootstrap procedure consistently performs well and it is about a percentage point 
closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse, with coverage as low as 31\% (in the second DGP) and never
higher than 86\%.

Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
similarly and have coverage close to the nominal level. The bootstrap explicitly
accounts for heterosedasticity in the DGP; CCT's procedure implicitly accomodates
smooth heteroskedasticity by estimating the variance in a neighborhood around
the cutoff.

The final column, ``CI Length,'' indicates that intervals from the
two robust procedures have average lengths close to each other in all of the DGPs,
while interval from the naive procedure is much shorter on average.

These are DGPs where the naive confidence intervals are known to perform poorly
and this set of simulation results indicates that our proposed bootstrap approach is 
competitive with analytical methods for producing robust intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs
and performs similarly well compared to the analytical bias correction procedures proposed by CCT.
